SecFFT: Safeguarding Federated Fine-tuning for Large Vision Language Models against Covert Backdoor Attacks in IoRT Networks

### 2024-11-12 response.tex

\textcolor{blue}{SecFFT outperforms other mechanisms in handling various attack. SecFFT achieves the lowest misidentification rate, at only 0.2\%, indicating its superior defense capability and robustness across various attack scenarios, accurately distinguishing between malicious and benign nodes. Conversely, the misidentification rates of Flame, FLTrust, and FoolsGold are 8\%, 3.9\%, and 9.5\%, respectively, with misidentified nodes more broadly distributed. Among them, FoolsGold exhibits the highest misidentification rate. It is worth noting that these statistical results align precisely with the findings from the previous experiment, further validating SecFFT's superior performance in instantaneous Attack Behavior Perception.}

Second, to improve the visibility and distinguish-ability of the partitioning results in Figure 6, we have added a supplementary sub-image that provides a clearer presentation of the partitioned sections. We also increased the font size to enhance readability, ensuring that key features are visible and easy to interpret. For details, please refer to Figure \ref{fig:lab1} and responses to the comment 2 from Reviewer 2.

Third, we re-adjusted the layout of Figure 7 to address the issues you pointed out. Specifically, we improved the font sizes, added necessary labels, and modified the legend for better comprehension. These adjustments were made to ensure that the experimental data in Figure 7 are both readable and visually clear. For details, please refer to Figure \ref{fig:lab2}.

% 修改后的结果如图\ref{fig:lab2}所示，同时我们也修改了文章中相应的分析部分，使其更易符合实验结果并且更易理解。
\begin{figure*}[!h]
    \centering
    \includegraphics[width=1\linewidth]{figures/lab2-combined.pdf}
    \caption{Visualization of node identification results under three attack scenarios (MR, EDGE CASE, NEUR) for four defense mechanisms (SecFFT, Flame, FLTrust, FoolsGold) using t-SNE. The F represent mis-identification, including both malicious nodes incorrectly identified as benign, or vice versa. }
    \label{fig:lab2}
\end{figure*}

% 对于Figure 7也是一样的，我们增加了对Figure 7的标题描述、文字分析等。

Similarly, for Figure 7, we have enhanced its description with a detailed caption, textual analysis, and additional explanations. This figure further illustrates the experimental outcomes across different defense methods under various attack scenarios. By providing a comprehensive breakdown of the visualized data and the implications of the results, we aim to ensure a clear understanding of the comparative performance of the algorithms. The improvements emphasize the nuances in the algorithms' behavior, highlighting their strengths and limitations under constrained and unconstrained conditions. The following are the corresponding modifications in the article:

\textcolor{blue}{As shown in Figure \ref{fig:lab3}, the Foolsgold defense algorithm exhibits moderate performance against EdgeCase attacks. While it can generally identify similar behaviors among benign bot nodes, its effectiveness is limited. The size constraint does not affect the cosine similarity calculations, but with both size and angle constraints applied, Foolsgold fails to defend effectively. For the FLTrust defense algorithm, its performance against EdgeCase attacks slightly surpasses that of Foolsgold; however, a certain degree of similarity remains between malicious and benign bot nodes. The size constraint has no impact on FLTrust's defense, but the combined constraints of size and angle significantly weaken its effectiveness, rendering it unable to correctly identify malicious nodes. The Flame defense algorithm relies on the HDBSCAN clustering method for identification. During clustering, Flame assigns nearly identical (or even identical) scores to clients of the same category, resulting in heatmaps that appear uniform and visually clear. However, the clustering results are fundamentally flawed. For instance, in the figure, clients 25, 46, and 47 display streaks of different colors, which, although faint, indicate incorrectly classified bot nodes. In contrast, the SecFFT defense algorithm leverages similarity calculations based on intent points. Under EdgeCase attacks, SecFFT can accurately identify malicious bot nodes, while the similarity among benign bot nodes remains low. The size constraint has minimal impact on SecFFT's performance, and even with size and angle constraints applied, the algorithm maintains robust similarity classification and achieves perfect accuracy.}

\begin{figure*}[!t]
    \centering
    \includegraphics[width=\linewidth]{figures/lab3-combined.pdf}
    % \caption{攻击防御实验结果图。第一列到第四列分别代表防御方式Foolsgold、FLTrust、Flame和SecFFT，第一行到第三行分别代表攻击方式EdgeCase、限制大小的EdgeCase、限制大小和角度的EdgeCase。每个实验中有50个客户端，其中0-19号是恶意客户端，每个子图中颜色越红代表识别结果越相似，越蓝代表识别结果越不相似。第一列绘图依据是Foolsgold防御算法中基于余弦相似度计算出来的wv值，第二列绘图依据是FLTrust防御算法中依据余弦相似度和relu激活函数计算出来的聚合权重，第三列绘图依据是Flame算法聚类时所采用的HDBSCAN算法的评分，第四列绘图依据是我们提出的SecFFT算法依据意图点进行相似度计算得到的评分。虽然Flame算法看起来相同种类客户端之间分数较为类似，但实际上其聚类时有明显的聚类错误。}
    \caption{\textcolor{blue}{The experimental results of attack defense are illustrated in the figures. The first to fourth columns represent the defense methods \cite{foolsgold}, FLTrust\cite{FLTrust}, Flame\cite{FLAME}, and SecFFT, respectively, while the first to third rows represent the attack methods EdgeCase\cite{EDGE_CASE}, size-constrained EdgeCase, and EdgeCase constrained by both size and angle. Each experiment involves 50 clients, among which clients numbered 0–19 are malicious. In each subplot, the redder the color, the more similar the identification results, and the bluer the color, the less similar they are. The first column visualizes the results based on the wv values calculated using cosine similarity in the Foolsgold defense algorithm. The second column is based on the aggregation weights computed by the FLTrust defense algorithm using cosine similarity and the ReLU activation function. The third column visualizes scores obtained from the HDBSCAN algorithm used for clustering in the Flame defense method. The fourth column shows scores derived from the similarity calculation based on intent points in the proposed SecFFT algorithm. Although the Flame algorithm appears to produce more similar scores among the same type of clients, it exhibits evident clustering errors during its clustering process.}}
    \label{fig:lab3}
\end{figure*}

### 2024-11-12 main-v2.tex
response: whom do I really response for?
Signed-off-by: LetMeFly666 <814114971@qq.com>

\begin{figure}[!t]
    \centering
    \includegraphics[width=\linewidth]{figures/fig4.jpg}
    \caption{Benign and Malicious Nodes Before Aggregation}
    \label{fig:before-agg}
\end{figure}
% 如图\ref{fig:before-agg}所示展示了异常检测和梯度聚合的计算流程示意图。图中每个球都是某个节点的意图范围。蓝色的球代表良性节点，红色的球代表异常节点。在进行异常检测时我们只考虑每个节点的意图点，即图中的球心位置。在计算可达距离时，由于意图点$O_{j_1}$距离意图点$O_i$较近，故二者之间的可达距离为意图点$O_i$的$q$距离$\widetilde{dis_i^q}$；由于意图点$O_{j_2}$距离$O_i$较远，所以二者之间的可达距离为二者之间的实际距离$\|O_i-O_{j_2}\|$。意图点$O_i$的密度高于其邻域意图点的密度，$lof_i<1$；而意图点$O_{j_2}$的密度低于其邻域意图点的密度，因此$lof_{j_2} > 1$。
As shown in Figure \ref{fig:before-agg}, the diagram illustrates the computational process of anomaly detection and gradient aggregation. Each sphere in the figure represents the intention range of a specific node. The blue spheres represent benign nodes, while the red spheres represent anomalous nodes. During anomaly detection, we only consider the intention point of each node, which is represented by the center of each sphere in the figure. When calculating the reachable distance, since intention point $O_{j_1}$ is close to intention point $O_i$, the reachable distance between them is the $q$-distance $\widetilde{dis_i^q}$ of intention point $O_i$. Since intention point $O_{j_2}$ is far from $O_i$, the reachable distance between them is the actual distance $\|O_i-O_{j_2}\|$ between them. The density of intention point $O_i$ is higher than that of its neighboring intention points, so $lof_i < 1$. On the other hand, the density of intention point $O_{j_2}$ is lower than that of its neighboring intention points, so $lof_{j_2} > 1$.

@@

\begin{figure*}[!t]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/lab2-combined.pdf}
    \caption{Visualization of node identification results under three attack scenarios (MR, EDGE CASE, NEUR) for four defense mechanisms (SecFFT, Flame, FLTrust, FoolsGold) using t-SNE. The red dots represent misidentified nodes, including both malicious nodes incorrectly identified as benign, or vice versa. }
    \label{fig:lab2}
\end{figure*}

@@

\begin{figure*}[!t]
    \centering
    \includegraphics[width=\linewidth]{figures/lab3-combined.pdf}
    \caption{Detection performance of different defense technologies against intelligent attackers with sophisticated multi-round strategies}
    \label{fig:lab3}
\end{figure*}

@@

>>>>

\begin{figure}[!t]
    \centering
    \includegraphics[width=\linewidth]{figures/fig4.pdf}
    \caption{Benign and Malicious Nodes Before Aggregation}
    \label{fig:before-agg}
\end{figure}
% 如图\ref{fig:before-agg}所示展示了异常检测和梯度聚合的计算流程示意图。图中每个球都是某个节点的意图范围。蓝色的球代表良性节点，红色的球代表异常节点。在进行异常检测时我们只考虑每个节点的意图点，即图中的球心位置。在计算可达距离时，由于意图点$O_{j_1}$距离意图点$O_i$较近，故二者之间的可达距离为意图点$O_i$的$q$距离$\widetilde{dis_i^q}$；由于意图点$O_{j_2}$距离$O_i$较远，所以二者之间的可达距离为二者之间的实际距离$\|O_i-O_{j_2}\|$。意图点$O_i$的密度高于其邻域意图点的密度，$lof_i<1$；而意图点$O_{j_2}$的密度低于其邻域意图点的密度，因此$lof_{j_2} > 1$。
As shown in Figure \ref{fig:before-agg}, the diagram illustrates the computational process of anomaly detection and gradient aggregation. Each sphere in the figure represents the intention range of a specific node. The blue spheres represent benign nodes, while the red spheres represent anomalous nodes. During anomaly detection, we only consider the intention point of each node, which is represented by the center of each sphere in the figure. When calculating the reachable distance, since intention point $O_{j_1}$ is close to intention point $O_i$, the reachable distance between them is the $q$-distance $\widetilde{dis_i^q}$ of intention point $O_i$. Since intention point $O_{j_2}$ is far from $O_i$, the reachable distance between them is the actual distance $\|O_i-O_{j_2}\|$ between them. The density of intention point $O_i$ is higher than that of its neighboring intention points, so $lof_i < 1$. On the other hand, the density of intention point $O_{j_2}$ is lower than that of its neighboring intention points, so $lof_{j_2} > 1$.

@@

\begin{figure*}[!t]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/lab2-combined.pdf}
    \caption{Visualization of node identification results under three attack scenarios (MR, EDGE CASE, NEUR) for four defense mechanisms (SecFFT, Flame, FLTrust, FoolsGold) using t-SNE. The F represent mis-identification, including both malicious nodes incorrectly identified as benign, or vice versa. }
    \label{fig:lab2}
\end{figure*}

@@

\begin{figure*}[!t]
    \centering
    \includegraphics[width=\linewidth]{figures/lab3-combined.pdf}
    % \caption{攻击防御实验结果图。第一列到第四列分别代表防御方式Foolsgold、FLTrust、Flame和SecFFT，第一行到第三行分别代表攻击方式EdgeCase、限制大小的EdgeCase、限制大小和角度的EdgeCase。每个实验中有50个客户端，其中0-19号是恶意客户端，每个子图中颜色越红代表识别结果越相似，越蓝代表识别结果越不相似。第一列绘图依据是Foolsgold防御算法中基于余弦相似度计算出来的wv值，第二列绘图依据是FLTrust防御算法中依据余弦相似度和relu激活函数计算出来的聚合权重，第三列绘图依据是Flame算法聚类时所采用的HDBSCAN算法的评分，第四列绘图依据是我们提出的SecFFT算法依据意图点进行相似度计算得到的评分。虽然Flame算法看起来相同种类客户端之间分数较为类似，但实际上其聚类时有明显的聚类错误。}
    \caption{\textcolor{red}{The experimental results of attack defense are illustrated in the figures. The first to fourth columns represent the defense methods \cite{foolsgold}, FLTrust\cite{FLTrust}, Flame\cite{FLAME}, and SecFFT, respectively, while the first to third rows represent the attack methods EdgeCase\cite{EDGE_CASE}, size-constrained EdgeCase, and EdgeCase constrained by both size and angle. Each experiment involves 50 clients, among which clients numbered 0–19 are malicious. In each subplot, the redder the color, the more similar the identification results, and the bluer the color, the less similar they are. The first column visualizes the results based on the wv values calculated using cosine similarity in the Foolsgold defense algorithm. The second column is based on the aggregation weights computed by the FLTrust defense algorithm using cosine similarity and the ReLU activation function. The third column visualizes scores obtained from the HDBSCAN algorithm used for clustering in the Flame defense method. The fourth column shows scores derived from the similarity calculation based on intent points in the proposed SecFFT algorithm. Although the Flame algorithm appears to produce more similar scores among the same type of clients, it exhibits evident clustering errors during its clustering process.}}
    \label{fig:lab3}
\end{figure*}

@@

% 由图\ref{fig:lab3}可以明显看出，FoolsGold防御算法对EdgeCase攻击的防御效果较为一般，但是基本上能看出良性机器人节点之间的行为较为类似。限制大小对余弦相似度的计算结果不会产生影响，但是限制大小和角度后可以发现Foolsgold算法已经无法成功防御。对于FLTrust防御算法，其在EdgeCase攻击下的防御效果较FoolsGold略好，但恶意机器人节点和良性机器人节点之间仍有一定程度的相似性。限制大小对FLTrust的防御效果没有影响，但是限制大小和角度后，FLTrust算法的防御效果明显下降，已经无法做到准确识别。对于Flame防御算法，其识别依据是HDBSCAN的聚类方式。在聚类时，Flame算法对于相同类别的客户端所赋的分数十分接近（甚至相同），因此导致绘制出来的热力图效果看起来较为均匀明了。但实际上，Flame的聚类结果直接是错误的，例如图中的客户端25、46、47能够看到有不同颜色的条纹。虽然这些条纹颜色较浅，但实际上这些都是识别错误的机器人节点。对于SecFFT防御算法，其识别依据是基于意图点的相似度计算。在EdgeCase攻击下，SecFFT算法能够准确识别出恶意机器人节点，而良性机器人节点之间的相似性较低。限制大小对SecFFT的防御效果几乎没有影响，并且限制大小和角度后SecFFT算法仍然能够保持一个不错的相似度分类效果以及完美的正确率。

\textcolor{red}{As shown in Figure \ref{fig:lab3}, the Foolsgold defense algorithm exhibits moderate performance against EdgeCase attacks. While it can generally identify similar behaviors among benign bot nodes, its effectiveness is limited. The size constraint does not affect the cosine similarity calculations, but with both size and angle constraints applied, Foolsgold fails to defend effectively. For the FLTrust defense algorithm, its performance against EdgeCase attacks slightly surpasses that of Foolsgold; however, a certain degree of similarity remains between malicious and benign bot nodes. The size constraint has no impact on FLTrust's defense, but the combined constraints of size and angle significantly weaken its effectiveness, rendering it unable to correctly identify malicious nodes. The Flame defense algorithm relies on the HDBSCAN clustering method for identification. During clustering, Flame assigns nearly identical (or even identical) scores to clients of the same category, resulting in heatmaps that appear uniform and visually clear. However, the clustering results are fundamentally flawed. For instance, in the figure, clients 25, 46, and 47 display streaks of different colors, which, although faint, indicate incorrectly classified bot nodes. In contrast, the SecFFT defense algorithm leverages similarity calculations based on intent points. Under EdgeCase attacks, SecFFT can accurately identify malicious bot nodes, while the similarity among benign bot nodes remains low. The size constraint has minimal impact on SecFFT's performance, and even with size and angle constraints applied, the algorithm maintains robust similarity classification and achieves perfect accuracy.}
